Dinner

### 2022-04-15 Memo/memo.Rmd
add large text revision

---
title: 
to:
from: 
date: "`r Sys.time()`"
output: 
  pdf_document:
    template: article-template.latex
bibliography: references.bib

---

We would like to thank the editor and three reviewers for their thoughtful consideration of our manuscript. We endeavored to incorporate the changes you suggested, and we believe our manuscript is much improved as a result. Below, we intersperse our reactions and revisions to the suggestions enumerated in the editor's decision letter and the three manuscript reviews. We adopt the following conventions:

>>>>

---
title: 
date: "`r Sys.time()`"
output: 
  pdf_document:
    template: memo-template.latex
bibliography: references.bib 
---

\noindent Dear Editors and Reviewers,
\vspace{.5cm}

\noindent We would like to thank you all for the opportunity to revise our
manuscript, "Legislature Size and Welfare: Evidence from Brazil" (Ms. No.
AJPS-44979). We have made several revisions to the paper along the lines
suggested by the editors and reviewers and we believe the manuscript has
improved significantly as a result.

We have also incorporated additional literature into the manuscript, which has
indeed given the paper a clearer theoretical framework through which our
results can be interpreted.

Below we discuss in more detail these changes and the several other changes we
have made to the manuscript in response to comments from the editors and
reviewers. We thank the editors again for the opportunity to revise the
manuscript, and the reviewers for their extremely helpful comments.

\vspace{.5cm}
\noindent Sincerely,

\vspace{.2cm}
\noindent The Authors

\newpage

the editor and the three anonymous reviewers for their thoughtful consideration of our manuscript. We endeavored to incorporate the changes you suggested, and we believe our manuscript is much improved as a result. Below, we intersperse our reactions and revisions to the suggestions enumerated in the editor's decision letter and the three manuscript reviews. We adopt the following conventions:
